\vspace{-\baselineskip} Fast and scalable Gaussian process modeling with applications to astronomical time series \vspace{-2\baselineskip}

### 2017-09-18 paper/response.txt

We would first like to thank the referee for their thorough and constructive
review. We have taken the feedback to heart and we think that the manuscript
has been greatly improved as a result. To simplify a second review, all major
changes are colored blue.

Beyond addressing each of the referee's concerns in detail, we have also
derived a new algorithm for solving celerite models that is about a factor of
20 faster than the submitted version (and about and order of magnitude faster
than a reference implementation of a Kalman filter based method). We have
updated the manuscript to describe and test this new method in Section 5. We
hope that the referee will consider this updated method and we welcome any
feedback.

@@

For each of the above, we agree and have addressed each concern.

### 2017-09-19 paper/ms.tex
formatting
typo

\section{The celerite model}\sectlabel{celerite}

@@

\subsection{Scalable computation of celerite models}\sectlabel{scalable}

@@

We then sample the joint posterior probability (\eqalt{joint-post}) using
\emcee\ \citep{Goodman:2010, Foreman-Mackey:2013}.
We initialize \exampleinwalkers~walkers\footnote{\responseb{``Walker'' is the
name given by \citet{Goodman:2010} and \citet{Foreman-Mackey:2013} to each
parallel MCMC chain in the ensemble sampling algorithm used in \emcee.}} by
sampling from a three-dimensional isotropic Gaussian centered the MAP
parameter vector and with a standard deviation of $10^{-4}$ in each dimension.
We then run \exampleinburn~steps of burn-in and \exampleinsteps~steps of MCMC.
To assess convergence, we estimate the integrated autocorrelation time of the
chain \responseb{averaged across parameters} \citep{Sokal:1989, Goodman:2010}
and find that the chain results in \exampleineff~effective samples.

@@

\newpage
\subsection{Code availability}

>>>>

\newpage
\section{The celerite model}\sectlabel{celerite}

@@

\newpage
\subsection{Scalable computation of celerite models}\sectlabel{scalable}

@@

We then sample the joint posterior probability (\eqalt{joint-post}) using
\emcee\ \citep{Goodman:2010, Foreman-Mackey:2013}.
We initialize \exampleinwalkers~walkers\footnote{\responseb{``Walker'' is the
name given by \citet{Goodman:2010} and \citet{Foreman-Mackey:2013} to each
parallel MCMC chain in the ensemble sampling algorithm used in \emcee.}} by
sampling from a three-dimensional isotropic Gaussian centered the on MAP
parameter vector and with a standard deviation of $10^{-4}$ in each dimension.
We then run \exampleinburn~steps of burn-in and \exampleinsteps~steps of MCMC.
To assess convergence, we estimate the integrated autocorrelation time of the
chain \responseb{averaged across parameters} \citep{Sokal:1989, Goodman:2010}
and find that the chain results in \exampleineff~effective samples.

@@

\subsection{Code availability}
